Adaptive Scheduling of Scientific Workflows

### 2024-03-22 main.tex
notes on small examples

We also keep track of the current memory usage, $\curM_j$ and $\curC_j$,
on respectively the processor memory and communication buffer. 
Furthermore, $\PD_j$ is a priority queue with the {\em pending data} 
that are in $\MM_j$ but may be evicted to be communicated, if 
more memory is needed on~$p_j$. They are ordered by non-decreasing size. 
They correspond to some $c_{u,v}$'s.

@@

>>>>

We also keep track of the current memory usage, $\curM_j$ and $\curC_j$,
on respectively the processor memory and communication buffer. 
Furthermore, $\PD_j$ is a priority queue with the {\em pending data} 
that are in the memory of size $\MM_j$ but may be evicted to be communicated, if 
more memory is needed on~$p_j$. They are ordered by non-decreasing size. 
They correspond to some $c_{u,v}$'s.

@@

\subsection{Approximation}
\hmey{Rough notes:}
Let's use a fork to see how the algorithm behaves and if it provides some approximation. Our current intuition is that, if the memory constraint is ignored, HEFTM-BLc provides a $2$-approximation (to be proved).
